---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: 
        latex_engine: xelatex
  github_document: 
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidymodels)
wine <- read_csv("winemag-data-130k-v2.csv") %>% select(-X1,-description,-taster_name, -taster_twitter_handle)
```
# Intro
Following [Julia Silge's guide](https://juliasilge.com/blog/intro-tidymodels/), I decided to try to predict the score of wine, using the [Wine Reviews dataset](https://www.kaggle.com/zynicide/wine-reviews) from Kaggle. 

## Summary
First, just let's look at the data. 
```{r Summary}
library(skimr)
skim(wine)
```

There's a lot of missing values all over. This needs to be dealt with, in some form. 

## EDA
Then, lets see if we can see something interesting by plotting the points by country in a box plot. For ease of reading, I've sorted the boxplot with the highest mean in descending order. Thanks to the R4DS slack-group for helping me with this!

```{r Boxplot}
wine %>% 
        drop_na(country) %>%
        mutate(country = fct_reorder(country, .x = points, .fun = mean)) %>% 
        ggplot(aes(x=country, y=points)) +
        geom_boxplot()+
        coord_flip()
```

And I don't know about you, but I was higly surpriced to see that England and India were the two countries with the on average best wines!

# Building a model
Now, let's build a model! First let's drop the NA's. Sadly, I don't know much imputation yet, so this is the way it has to be(for now!).
Then split it into training and testing sets.
```{r Splitting}
wine <- wine %>% drop_na() %>% select(points, price, country) %>%
  mutate(country = as.factor(country))
set.seed(1234)
wine_split <- initial_split(wine)

wine_test <- testing(wine_split)
wine_train <- training(wine_split)
```


## Specs 
Using a Random Forest in regression mode, we set the engine to use the ranger package. 
```{r Setting Specs}
rf_spec <- rand_forest(mode = "regression") %>%
        set_engine("ranger")
rf_spec
```

## Fitting
Then let's fit it, using `points` as the target and every other variable as a predictor. 
```{r Fitting}
rf_fit <- rf_spec %>%
        fit(points ~.,
            data=wine_train)
rf_fit
```

## Results
So, let's look at the results!
```{r Results}
results_train <- rf_fit %>%
  predict(new_data = wine_train) %>%
  mutate(truth = wine_train$points) %>% 
        rmse(truth = truth, estimate = .pred) %>% 
        mutate(split = "training")

results_test <- rf_fit %>%
  predict(new_data = wine_test) %>%
  mutate(truth = wine_test$points) %>% 
        rmse(truth = truth, estimate = .pred) %>% 
        mutate(split = "test")

results <- results_train %>% bind_rows(results_test)
results
```
Sadly, as we can see, the model seem to have been overfitted to the training data. Let's correct that!

## Cross validating

```{r Cross Validation, eval=FALSE}
set.seed(1234)
wine_folds <- vfold_cv(wine_train)

rf_res <- fit_resamples(
  points ~ .,
  rf_spec,
  wine_folds)

rf_res %>%
  collect_metrics()
```

which sadly gives me the following error:
x Fold01: formula: Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]): contrasts can be applied only to factors with 2 or more...
x Fold02: formula: Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]): contrasts can be applied only to factors with 2 or more...
x Fold03: formula: Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]): contrasts can be applied only to factors with 2 or more...
x Fold04: formula: Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]): contrasts can be applied only to factors with 2 or more...
x Fold05: formula: Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]): contrasts can be applied only to factors with 2 or more...
x Fold06: formula: Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]): contrasts can be applied only to factors with 2 or more...
x Fold07: formula: Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]): contrasts can be applied only to factors with 2 or more...
x Fold08: formula: Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]): contrasts can be applied only to factors with 2 or more...
x Fold09: formula: Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]): contrasts can be applied only to factors with 2 or more...
x Fold10: formula: Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]): contrasts can be applied only to factors with 2 or more...
All models failed in [fit_resamples()]. See the `.notes` column.

Any ideas?












